---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rpolecat

<!-- badges: start -->
<!-- badges: end -->

The goal of rpolecat is to make downloading and working with the [POLECAT event data](https://dataverse.harvard.edu/dataverse/POLECAT) easier. 

The POLECAT data are provided via two repositories on dataverse:

- [POLECAT Weekly Data](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/AJGVIT), containing the actual data files. 
- [POLECAT Documentation](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LMFPIP)

## Installation

You can install the development version of rpolecat like so:

``` r
library(remotes)
install_github("basil-analytics/rpolecat")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rpolecat)

data(contexts)
head(contexts)

data(modes)
head(modes)
```

To download the data:

```{r eval=FALSE}
# (not run)

# to donwload all data
download_polecat(local_dir = "foo/foo")

# to download only some years
download_polecat(local_dir = "foo/foo", years = c(2021:2023))
```

## Data license

The data license is [viewable on dataverse](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/AJGVIT). We copy it here for convenience:

> The POLECAT data are produced by the Program on Geostrategic Risk (formerly the Political Instability Task Force). The Program on Geostrategic Risk is funded by the Central Intelligence Agency. The views expressed are the authors' alone and do not represent the views of the U.S. Government. We are unable to provide the story text from which events are extracted or the URLs due to licensing restrictions. For any data issues or bug reports please contact the dataset points of contact. THESE MATERIALS ARE SUBJECT TO COPYRIGHT PROTECTION AND MAY ONLY BE USED AND COPIED FOR RESEARCH AND EDUCATIONAL PURPOSES. THE MATERIALS MAY NOT BE USED OR COPIED FOR ANY COMMERCIAL PURPOSES. © 2023 Leidos. All rights reserved. THE MATERIALS ARE PROVIDED ON AN AS-IS BASIS, WITH NO WARRANTIES OR GUARANTIES OF ANY KIND. THE OWNERS WILL NOT BE LIABLE FOR ANY DAMAGES ARISING FROM THEIR USE. USE OF THE MATERIALS IS ENTIRELY AT YOUR OWN RISK.



